\documentclass[a4paper,11pt]{article}
\usepackage[left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm]{geometry}
\usepackage{url,parskip}
\usepackage{microtype}
\usepackage[dvipsnames]{xcolor}
\usepackage{titlesec}
\usepackage{etaremune}
\usepackage{doi}    
\usepackage[english]{babel} 
\usepackage[none]{hyphenat}     
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}
\titleformat{\section}
  {\normalfont\large\bfseries}
  {}
  {0pt}
  {}
  
\setlength{\parskip}{0.3em}
\setlength{\parindent}{0pt}

\begin{document}
\pagestyle{empty}
\sloppy

%--------------------TITLE-------------
{\centering{\Large \textbf{Raymond Boadi Frempong}}\par}
{\centering Associate Professor (Maître de Conférences)\par}
\vspace{0.3em}

%--------------------SECTIONS-----------------------------------
\section*{Personal Data}
\begin{tabular}{@{}p{2.8cm}p{11.5cm}@{}}
Affiliation: & European School of Political and Social Sciences, Catholic University of Lille, France. \\
Email:   & \href{mailto:raymond.frempong@univ-catholille.fr}{raymond.frempong@univ-catholille.fr}. \\
ORCID:   & \href{https://orcid.org/0000-0002-4603-5570}{0000-0002-4603-5570}. \\
Website: & \href{https://rfrempong.github.io/raymondbfrempong.github.io/}{rfrempong.github.io}.\\
\end{tabular}

\section*{Education}
\begin{tabular}{@{}p{2.8cm}p{11.5cm}@{}}
2014--2018 & \textbf{PhD (Economics), \textit{with Distinction}}, University of Bayreuth, Germany. \\
2011--2013 & \textbf{MPhil (Economics)}, University of Cape Coast, Ghana. \\
2004--2008 & \textbf{B.A. (Social Sciences, Economics)}, University of Cape Coast, Ghana. 
\end{tabular}

\section*{Research Profile}
Dr. Frempong applies microdata and econometric methods to explore how behavioral traits, environmental factors, and policy interventions shape development outcomes in the Global South. His research spans food security, natural resource economics, health, and education, with emphasis on gender, ethnicity, and vulnerable groups.

\section*{Academic Positions}
\begin{tabular}{@{}p{2.8cm}p{11.5cm}@{}}
2023--present & \textbf{\textit{Maître de Conférences} in Development Economics}, European School of Political and Social Sciences, Catholic University of Lille, France. \\[0.3em]

2019--2023 & \textbf{Postdoctoral Researcher}, Chair of Economic Policy and Economic Development, University of Bayreuth, Germany. 

Project: \textit{Multiplicity in Decision-Making of Africa's Interacting Markets: The Functioning of Community Law, the Role of Market Participants and the Power of Regional Judges}. \\[0.3em]

2009--2011 & \textbf{Economics and Social Studies Teacher}, Ghana Christian International High School. 

Subjects: Cambridge O'Level/A'Level Economics, WASSCE Economics, Social Studies. \\[0.3em]

2008--2009 & \textbf{Teaching Assistant}, Department of Economics, University of Cape Coast, Ghana. 

Duties: Tutorial organization, test/examination marking. \\
\end{tabular}

\section*{Peer-Reviewed Journal Publications}

\begin{enumerate}

\item \textbf{Frempong, R.~B.}, Stadelmann, D., \& Thiam, D.~R. (2025). How do current and past mining activities affect water security and health. \textit{Applied Economic Perspectives and Policy}. \doi{10.1002/aepp.13510}.

\item \textbf{Frempong, R.~B.}, \& Stadelmann, D. (2024). Exploring education-induced bargaining power of women on household welfare in Sub-Saharan Africa. \textit{Economies}, 12(11), 293. \doi{10.3390/economies12110293}.

\item \textbf{Frempong, R.~B.}, Stadelmann, D., \& Thiam, D.~R. (2024). Clean energy adoption in developing countries: New evidence of the relevance of risk aversion and education. \textit{Journal of Development Studies}. \doi{10.1080/00220388.2024.2407820}.

\item \textbf{Frempong, R.~B.}, Gross, E., \& Owusu, V. (2023). Crop diversity, sustainable food and nutritional security among smallholder farmers in Ghana. \textit{British Food Journal}. \doi{10.1108/BFJ-12-2022-1060}.

\item Kofinti, R., Orkoh, E., \textbf{Frempong, R.~B.}, \& Annim, S.~K. (2023). Firms' digital investment and resilience to shocks: Evidence from the COVID-19 pandemic in Ghana. \textit{Journal of International Development}. \doi{10.1002/jid.3769}.

\item Azevedo, F., Pavlović, T., Rêgo, G.~G.~d., Ay, F.~C., Gjoneska, B., Etienne, T., \ldots \textbf{Frempong, R.~B.} \ldots Sampaio, W.~M. (2023). Social and moral psychology of COVID-19 across 69 countries. \textit{Nature Scientific Data}, 10, 272. \doi{10.1038/s41597-023-02080-8}.

\item \textbf{Frempong, R.~B.} (2022). Do subsidies on seed and fertilizer lead to child labour? Evidence from Malawi. \textit{Development Policy Review}, 40(6), e12646. \doi{10.1111/dpr.12646}.

\item Pavlović, T., Azevedo, F., De, K., Riaño-Moreno, J.~C., Maglić, M., Gkinopoulos, T., \ldots \textbf{Frempong, R.~B.} \ldots Keudel, O. (2022). Predicting attitudinal and behavioral responses to COVID-19 pandemic using machine learning. \textit{PNAS Nexus}, 1(3), pgac093. \doi{10.1093/pnasnexus/pgac093}.

\item Van Bavel, J.~J., Cichocka, A., Capraro, V., Sjåstad, H., Nezlek, J.~B., Alfano, M., \ldots \textbf{Frempong, R.~B.} \ldots Hudecek, M.~F.~C. (2022). National identity predicts public health support during a global pandemic. \textit{Nature Communications}, 13, 517. \doi{10.1038/s41467-021-27668-9}.

\item \textbf{Frempong, R.~B.}, \& Stadelmann, D. (2021). Risk preference and child labor: Econometric evidence. \textit{Review of Development Economics}, 25(2), 878-894. \doi{10.1111/rode.12746}.

\item \textbf{Frempong, R.~B.}, Kitzmüller, L., \& Stadelmann, D. (2021). A micro-based approach to evaluate the effect of water supply on health in Uganda. \textit{World Development}, 145, 105522. \doi{10.1016/j.worlddev.2021.105522}.

\item \textbf{Frempong, R.~B.}, Orkoh, O., \& Kofinti, R.~E. (2021). Household's use of cooking gas and children's learning outcomes in rural Ghana. \textit{Energy Economics}, 103, 105617. \doi{10.1016/j.eneco.2021.105617}.

\item \textbf{Frempong, R.~B.}, Stadelmann, D., \& Wild, R. (2020). Coronavirus lockdowns, secondary effects and sustainable exit-strategies for sub-Saharan Africa. \textit{Economics Bulletin}, 40(3), 2586-2593.

\item \textbf{Frempong, R.~B.}, \& Stadelmann, D. (2019). The effect of food prices on child labour among farm households: Evidence from Uganda. \textit{Journal of Development Studies}, 55(7), 1492-1507. \doi{10.1080/00220388.2018.1448066}.

\item Stadelmann, D., \& \textbf{Frempong, R.~B.} (2018). Did the customs union of the East African Community increase overall trade of Kenya, Tanzania and Uganda? \textit{The African Review}, 45(2), 348-361.

\item Annim, S.~K., \& \textbf{Frempong, R.~B.} (2018). Effects of access to credit and income on dietary diversity in Ghana. \textit{Food Security}, 10(6), 1649-1663. \doi{10.1007/s12571-018-0862-8}.

\item \textbf{Frempong, R.~B.}, \& Annim, S.~K. (2017). Dietary diversity and child malnutrition in Ghana. \textit{Heliyon}, 3(5), e00298. \doi{10.1016/j.heliyon.2017.e00298}.

\end{enumerate}

\section*{Book Chapters}

\begin{enumerate}

\item Novignon, J., Gowokani, C.~C., \& \textbf{Frempong, R.~B.} (2024). Impact of agricultural input subsidy on nutritional outcomes in Malawi. In H. Chavula et al. (Eds.), \textit{The Oxford Handbook of the Malawi Economy}. Oxford University Press.

\item \textbf{Frempong, R.~B.}, Novignon, J., \& Stadelmann, D. (2023). Inequalities, exclusion, and COVID-19 in Sub-Saharan Africa. In S. Arndt et al. (Eds.), \textit{Covid-19 in Africa: Societal and Economic Implications} (pp. 129-156). Springer.

\item Novignon, J., \textbf{Frempong, R.~B.}, \& Afoakwah, C. (2017). Access to markets, food security and poverty in Ghana: Evidence from smallholder farmers. In W. Akpalu et al. (Eds.), \textit{Linking smallholder farmers to markets} (pp. 41-68). University of Nairobi Press.

\end{enumerate}

\section*{Working Papers \& Work in Progress}

\begin{enumerate}

\item \textbf{Frempong, R.~B.}, \& Frempong, F.~M. (2023). Natural resource extraction and inequality in West Africa. [Under review].

\item \textbf{Frempong, R.~B.}, Stadelmann, D., \& Thiam, D.~R. (2022). Mineral resources extraction, institutional quality and poverty: A micro evidence from Africa.

\item \textbf{Frempong, R.~B.}, Stadelmann, D., \& Wild, F. (2022). Ethnic identity and support for economic and political integration in Africa.

\item \textbf{Frempong, R.~B.}, Afoakwah, C., \& Ampofo, A. (2022). Farm input subsidy programs and subjective wellbeing: Quasi experimental evidence from Malawi.

\item \textbf{Frempong, R.~B.}, \& Gross, E. (2018). Food security and crop diversity among subsistence farmers.

\end{enumerate}

\section*{Policy Reports \& Other Publications}

\begin{enumerate}

\item Orkoh, E., \& \textbf{Frempong, R.~B.} (2024). Ghana 2021 Population and Housing Census Thematic Report on Non-monetary Poverty Dimensions. Report commissioned by the Ghana Statistical Service.

\item \textbf{Frempong, R.~B.}, \& Stadelmann, D. (2022, June). A micro-based evaluation of water projects. \textit{Long-Run Health Matters}. \url{https://lrhmatters.com/drivers-of-health/a-micro-based-evaluation-of-water-projects}.

\item Novignon, J., Gowokani, C.~C., \& \textbf{Frempong, R.~B.} (2021, October). Impact of agricultural input subsidy on nutritional outcomes in Malawi (Working Paper No. 778). African Economic Research Consortium.

\item Stadelmann, D., Wild, F., \& \textbf{Frempong, R.~B.} (2021, June). Every (immune) person counts, especially in developing countries. \textit{Observer Research Foundation}.

\end{enumerate}

\section*{Competitive Research Grants (Total: USD 39,000)}

\begin{enumerate}

\item Natural Resources and Inequality in West Africa (with Felicia Mabel Frempong). International Development Economists Associates (IDEAS), USD 5,000 (2022).

\item Socioeconomic and cultural drivers of women's formal work in rural Ghana (with Elena Gross). UNU-WIDER, USD 10,000 (2019--2020).

\item Impact of agricultural input subsidy on nutritional outcomes in Malawi (with Jacob Novignon and Chirwa Chijere Gowokani). African Economic Research Consortium, USD 12,000 (2018--2020).

\item Access to markets, food security and poverty in Ghana (with Jacob Novignon and Clifford Afoakwah). African Economic Research Consortium, USD 12,000 (2015--2016).

\end{enumerate}

\section*{Teaching Experience}

\textbf{Graduate courses:} Global Food Security; Economics of Child Labour; Agriculture and Rural Politics; Agricultural Interventions and Household Food and Nutrition Security; Women's Bargaining Power and Intra-Household Decision-Making.

\textbf{Undergraduate courses:} Environment, Resources, and Food; Principles of Microeconomics and Macroeconomics; Elements of Microeconomics and Macroeconomics; Public Economics; Politics of Development; Mathematics for Social Sciences.

\section*{Academic Service \& Supervision}

\begin{itemize}
\item \textbf{Editorial Board:} Member, \textit{Water Economics and Policy}.

\item \textbf{Supervision:} PhD mentorship team member (University of Bayreuth); 6 Master's theses (Catholic University of Lille, 2023--2025); 22 Bachelor's theses (Lille \& Bayreuth). One undergraduate thesis led to publication in \textit{World Development}.

\textbf{Selected Master's thesis topics:}
\begin{itemize}
\item Information Technology, Governance, Democracy \& Transparency in the African Union Countries: Lessons from the EU and UK (2025)
\item The Impact of International Trade Policies on Food Security in Sub-Saharan African Countries (2025)
\item The Securitization of Migration and its Political Impacts in the European Union: The Case of France (2025)
\item The Political Economy of Farm Food Waste in the Philippines (2024)
\item Conflict in Eastern Democratic Republic of Congo: Considering a New Perspective (2024)
\item Breaking Ground: Uncovering Barriers to Climate-Smart Agriculture Implementation in Southeast Asia (2024)
\end{itemize}

\item \textbf{Reviews:} External PhD examiner (University of Cape Town, 2022--present); DAAD proposal evaluator (4 proposals for Sub-Saharan African host institutions); Lindau Alumni peer reviewer; Journal reviewer for \textit{Energy Economics, International Economics, Journal of Development Studies, Kyklos, European Journal of Health Economics, German Economic Review}, among others.

\end{itemize}

\section*{Awards \& Honors}

\begin{itemize}
\item Visiting Scholar, School of Economics, University of Cape Town (2023).
\item Scholarship recipient, 6th Lindau Meeting on Economic Sciences (2017).
\item PhD scholarship, Bayreuth International Graduate School of African Studies (2014--2018).
\end{itemize}

\section*{Professional Development \& Training}

\begin{itemize}
\item Global flow, local fix Workshop, Accra, Ghana (2024).
\item Experimental Economics Summer Program, Paris School of Economics, France (2017).
\item Bavaria Graduate Program in Economics: Advanced Macroeconomics (2016); Empirical Evaluation Methods (2015); Advanced Microeconomics (2015); Advanced Econometrics (2015).
\item ICPSR Summer Programme, University of Michigan: Providing Social Science Services (2014); Curating and Managing Research Data for Re-Use (2014).
\item UNCTAD Workshop on Use of Stata in Analyzing Trade and Development Issues, University of Cape Coast, Ghana (2013).
\end{itemize}

\section*{Selected Conference Presentations}

\begin{itemize}
\item Eleventh Biennial Rosenberg International Forum on Water Policy, Cape Town, South Africa (2023).
\item African Studies Association of Africa 4th Biennial Conference, Cape Town, South Africa (2022).
\item African Economic Research Consortium Biannual Research Workshop, Cape Town, South Africa (2019).
\item Centre for the Study of African Economies (CSAE) Conference, Oxford, United Kingdom (2019, 2018).
\item African Economic Research Consortium Biannual Research Workshop, Arusha, Tanzania (2017).
\end{itemize}

\section*{Languages \& Technical Skills}

\begin{itemize}
\item \textbf{Languages:} Twi (native); English (professional); German (B1); French (A2, ongoing).
\item \textbf{Technical:} Stata, SPSS, CSPro; LaTeX, MS Office.
\end{itemize}

\end{document}
