\documentclass[a4paper,11pt]{article}
\usepackage[left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm]{geometry}
\usepackage{url,parskip}
\usepackage{microtype}
\usepackage[dvipsnames]{xcolor}
\usepackage{titlesec}
\usepackage{etaremune}
\usepackage{doi}    
\usepackage[english]{babel}        
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}
\titleformat{\section}
  {\normalfont\large\bfseries}
  {}
  {0pt}
  {}
  
\setlength{\parskip}{0.3em}
\setlength{\parindent}{0pt}

\begin{document}
\pagestyle{empty}
\sloppy  % Helps prevent overfull boxes

%--------------------TITLE-------------
{\centering{\Large \textbf{Raymond Boadi Frempong}}\par}
{\centering Associate Professor (Maître de Conférences)\par}
\vspace{0.3em}

%--------------------SECTIONS-----------------------------------
\section*{Personal Data}
\begin{tabular}{@{}p{2.8cm}p{11.5cm}@{}}
Affiliation: & European School of Political and Social Sciences, Catholic University of Lille, France. \\
Email:   & \href{mailto:raymond.frempong@univ-catholille.fr}{raymond.frempong@univ-catholille.fr}. \\
ORCID:   & \href{https://orcid.org/0000-0002-4603-5570}{0000-0002-4603-5570}. \\
Website: &  \href{https://rfrempong.github.io/raymondbfrempong.github.io/}{rfrempong.github.io}.\\
\end{tabular}

\section*{Education}
\begin{tabular}{@{}p{2.8cm}p{11.5cm}@{}}
2014--2018 & \textbf{PhD (Economics), \textit{with Distinction}}, University of Bayreuth, Germany. \\
2011--2013 & \textbf{MPhil (Economics)}, University of Cape Coast, Ghana. \\
2004--2008 & \textbf{B.A. (Social Sciences, Economics)}, University of Cape Coast, Ghana. 
\end{tabular}

\section*{Academic Positions}
\begin{tabular}{@{}p{2.8cm}p{11.5cm}@{}}
2023--present & \textbf{\textit{Maître de Conférences} in Development Economics}, Catholic University of Lille, France. \\
2019--2023 & \textbf{Postdoctoral Researcher}, Chair of Economic Policy and Economic Development, University of Bayreuth, Germany. \\
\end{tabular}

\section*{Selected Publications (from 19 peer-reviewed articles)}
\begin{enumerate}
\item \textbf{Frempong, R.~B.}, Stadelmann, D., \& Thiam, D.~R. (2025). How do current and past mining activities affect water security and health. \textit{Applied Economic Perspectives and Policy}. \doi{10.1002/aepp.13510}.

\item \textbf{Frempong, R.~B.}, Stadelmann, D., \& Thiam, D.~R. (2024). Clean energy adoption in developing countries: New evidence of the relevance of risk aversion and education. \textit{Journal of Development Studies}. \doi{10.1080/00220388.2024.2407820}.

\item \textbf{Frempong, R.~B.}, \& Stadelmann, D. (2024). Exploring education-induced bargaining power of women on household welfare in Sub-Saharan Africa. \textit{Economies}, 12(11), 293.

\item \textbf{Frempong, R.~B.} (2022). Do subsidies on seed and fertilizer lead to child labour? Evidence from Malawi. \textit{Development Policy Review}. \doi{10.1111/dpr.12646}.

\item Van Bavel, J.~J., Cichocka, A., Capraro, V., et al. (2022). National identity predicts public health support during a global pandemic. \textit{Nature Communications}, 13(517). \doi{10.1038/s41467-021-27668-9}.

\item \textbf{Frempong, R.~B.}, Kitzmüller, L., \& Stadelmann, D. (2021). A micro-based approach to evaluate the effect of water supply on health in Uganda. \textit{World Development}, 145, 105522.

\item \textbf{Frempong, R.~B.}, \& Stadelmann, D. (2019). The effect of food prices on child labour among farm households: Evidence from Uganda. \textit{Journal of Development Studies}, 55(7), 1492-1507.

\item Stadelmann, D., \& \textbf{Frempong, R.~B.} (2018). Did the customs union of the East African Community increase overall trade of Kenya, Tanzania and Uganda? \textit{The African Review}, 45(2), 348-361.
\end{enumerate}

\section*{Competitive Research Grants (Total: USD 39,000)}
\begin{enumerate}
\item Natural Resources and Inequality in West Africa. International Development Economists Associates (IDEAS), USD 5,000 (2022).

\item Socioeconomic and cultural drivers of women's formal work in rural Ghana. UNU-WIDER, USD 10,000 (2019--2020).

\item Impact of agricultural input subsidy on nutritional outcomes in Malawi. African Economic Research Consortium, USD 12,000 (2018--2020).

\item Access to markets, food security and poverty in Ghana. African Economic Research Consortium, USD 12,000 (2015--2016).
\end{enumerate}

\section*{Teaching Experience}
\textbf{Graduate courses:} Global Food Security; Economics of Child Labour; Agriculture and Rural Politics; Agricultural Interventions and Household Food and Nutrition Security; Women's Bargaining Power and Intra-Household Decision-Making. 

\textbf{Undergraduate courses:} Environment, Resources, and Food; Principles of Micro- and Macroeconomics; Public Economics; Politics of Development; Mathematics for Social Sciences.

\section*{Academic Service \& Supervision}
\begin{itemize}
\item \textbf{Editorial Board:} Member, \textit{Water Economics and Policy}.

\item \textbf{Supervision:} 6 Master's theses (Catholic University of Lille, 2023--2025); 22 Bachelor's theses (Lille \& Bayreuth); PhD mentorship team member (University of Bayreuth).

\item \textbf{Reviews:} External PhD examiner (University of Cape Town, 2022--present); DAAD proposal evaluator; Lindau Alumni peer reviewer; Journal reviewer for \textit{Energy Economics, Journal of Development Studies, Kyklos, European Journal of Health Economics, German Economic Review}, among others.
\end{itemize}

\section*{Awards \& Career Development}
\begin{itemize}
\item Visiting Scholar, School of Economics, University of Cape Town (2023).
\item Scholarship recipient, 6th Lindau Meeting on Economic Sciences (2017).
\item PhD scholarship, Bayreuth International Graduate School of African Studies (2014--2018).
\item Advanced training: Experimental Economics (Paris School of Economics); Advanced Econometrics, Microeconomics, Macroeconomics (Bavaria Graduate Program); Research Data Management (ICPSR, University of Michigan).
\end{itemize}

\section*{Languages \& Technical Skills}
\begin{itemize}
\item \textbf{Languages:} Twi (native); English (professional); German (B1); French (A2, ongoing).
\item \textbf{Technical:} Stata, SPSS, CSPro; LaTeX, MS Office.
\end{itemize}

\end{document}
